---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
Questions: 
how does savings relate to learning

look at baseline and learning
analyze the number of errors

Conclusions
- use new untrained sequences every time
- considerable transfer
- some train twice the same day or skip several days. Make it clear that we will catch them 
- longer from and to chords are more difficult: maximize 2 - 3  and 3 - 2 chords, and 2 - 3 over 3 - 2 
- unseen and untrained take the  same time: memorization does not make a difference


```{r}
rm(list=ls())

#if (!require("pacman")) install.packages("pacman")

#pacman::p_load(ggplot2, reshape2, dplyr, stringr)

library(ggplot2)
library(reshape2)
library(dplyr)
library(stringr)
library(boot)
library(lmPerm)
#library(GGally)
#library(network)
library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=native')
options(mc.cores = parallel::detectCores())
setwd("~/projects/SeqLearn/stats")

suffix = '20190113_1631-KIpilot1db'
keysfile = paste0('../data/archive/keys_table-', suffix, '.csv')
trialsfile = paste0('../data/archive/trials_table-', suffix, '.csv')
memofile = paste0('../data/archive/memo_table-', suffix, '.csv')

suffix0 = '20181126_2119-KIpilot0db'
keysfile0 = paste0('../data/archive/keys_table-', suffix0, '.csv')
trialsfile0 = paste0('../data/archive/trials_table-', suffix0, '.csv')
memofile0 = paste0('../data/archive/memo_table-', suffix0, '.csv')

suffix2 = '20181210_0918-LundfMRIpilot0db'
keysfile2 = paste0('../data/archive/keys_table-', suffix2, '.csv')
trialsfile2 = paste0('../data/archive/trials_table-', suffix2, '.csv')

keys.table1 = unique(read.table(keysfile, sep =';', header = T, quote = "")[-1])
keys.table1 = subset(keys.table1, !(username == 'kip1s006' & sess_num == 15))
trials.table1 = unique(read.table(trialsfile, sep =';', header = T,quote = "")[-1])
trials.table1 = subset(trials.table1, !(username == 'kip1s006' & sess_num == 15))
memo.table1 = unique(read.table(memofile, sep =';', header = T,quote = "")[-1])
memo.table1 = subset(memo.table1, !(username == 'kip1s006' & sess_num == 15))

keys.table2 = unique(read.table(keysfile2, sep =';', header = T, quote = "")[-1])
trials.table2 = unique(read.table(trialsfile2, sep =';', header = T,quote = "")[-1])

# remove some data 

trials.table0 = unique(read.table(trialsfile0, sep =';', header = T,quote = "")[-1])
trials.table0 = subset(trials.table0, username != 'kip0s001')
trials.table = rbind(trials.table1, trials.table0, trials.table2)

keys.table0 = unique(read.table(keysfile0, sep =';', header = T,quote = "")[-1])
keys.table0 = subset(keys.table0, username != 'kip0s001')
keys.table = rbind(keys.table1, keys.table0, keys.table2)

memo.table0 = unique(read.table(memofile0, sep =';', header = T,quote = "")[-1])
memo.table0 = subset(memo.table0, username != 'kip0s001')
memo.table = rbind(memo.table1, memo.table0)
#keys.melt = melt(keys.table, id.vars = c("cumulative_trial","trial","keystroke","response") )
#trials.melt = melt(keys.table, id.vars = c("cumulative_trial","trial","keystroke","response") )

```
Analyze chords

```{r fig.width=11, fig.asp=0.8}

ok_keys = subset(keys.table, paced == 0 & trial_type != "missing" & accuracy == 1 & keystroke > 0) %>%
  mutate(size_from = nchar(gsub(" ", "", key_from)), 
         size_to = nchar(gsub(" ", "", key_to)))

# baseline
ok_keys_baseline = subset(ok_keys, sess_num == 1 & trial < 5 )

  keys.table.median = ok_keys_baseline %>% group_by(username, key_from, key_to, size_from, size_to) %>% summarise(medianRT = median(RT), sdRT = sd(RT))

keys.table.median = keys.table.median %>% arrange(username, medianRT) %>% group_by(username) %>% mutate(rankRT = percent_rank(medianRT), transition= paste(key_from, key_to, sep = ' - '), size_trans = size_from + size_to, devRT = scale(medianRT, scale = F, center = T))

# rank within each subject
plot.median = ggplot(keys.table.median, aes(x = key_from, y = medianRT)) + 
    geom_errorbar(aes(ymin=medianRT-sdRT, ymax=medianRT+sdRT), width=.1) +
    geom_line() + 
    geom_point() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + facet_grid( . ~ username)
print(plot.median)

keys.table.rank = keys.table.median %>% group_by(key_from, key_to, size_from, size_to, transition, size_trans) %>% summarise(meandev = mean(devRT), meanrank = mean(rankRT), medianrank = median(rankRT), count = n(), minrank = min(rankRT), maxrank = max(rankRT)) %>% arrange(meanrank)

keys.table.rank = keys.table.rank %>% mutate(
         to1 = length(grep("1", key_to)),
         to2 = length(grep("2", key_to)),
         to3 = length(grep("3", key_to)),
         to4 = length(grep("4", key_to)),
         from1 = length(grep("1", key_from)),
         from2 = length(grep("2", key_from)),
         from3 = length(grep("3", key_from)),
         from4 = length(grep("4", key_from))
)

keys.table.rank = subset(keys.table.rank, count > 1)
plot.rank = ggplot(keys.table.median, aes(x = transition, y = rankRT, col = username)) + 
    geom_point() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
#print(plot.rank)
keys.table.rank$logmedianrank = logit(keys.table.rank$medianrank + 0.0001)
model.rank = lm(logmedianrank ~ size_from + size_to, data = keys.table.rank)
summary(model.rank)
model.rank = lm(logmedianrank ~ to1*to2 + to1*to3 + to1*to4 + to2*to3 + to2*to4 + to3*to4, data = keys.table.rank)
summary(model.rank)
model.rank = lm(logmedianrank ~ from1 + from2 + from3 + from4, data = keys.table.rank)
summary(model.rank)

plot(keys.table.rank$medianrank, lwd = 2, type = "l")
lines(keys.table.rank$minrank, lty = 2)
lines(keys.table.rank$maxrank, lty = 2)

#par(mfrow = c(1, 3))
# boxplot(keys.table.rank$medianrank ~ keys.table.rank$size_trans, main = "transition")
# boxplot(keys.table.rank$medianrank ~ keys.table.rank$size_from, main = "from")
# boxplot(keys.table.rank$medianrank ~ keys.table.rank$size_to, main = "to")
# 
# boxplot(keys.table.rank$medianrank ~ keys.table.rank$to1, main = "to_1")

# plot.keystrokepairs = ggplot(keys.table.rank, aes(x = key_from, y = key_to, fill = medianRT)) + geom_tile() + theme_classic()
# print(plot.keystrokepairs)


```
```{r}

learners = c("kip1s002", "kip1s003", "kip1s004", "kip1s005", "kip1s006", "kip1s008", "kip1s009", "lup0s002")

# learning
# subjects with 
ok_keys_learning = subset(ok_keys, trial > 5 & trial < 11 & username %in% learners )


learning_rate = function(y, plotit = F){ 
  x = seq(length(y)) - 1 
  m = lm(log(y) ~ x)   
#  print(coef(m))
  
  alpha = exp(coef(m)[1])
  beta = -coef(m)[2]

  if(plotit){
   print(length(y))   
   plot(x, y)
   lines(x, alpha*exp(-beta*x), col = 'red')
  }
  
  return(beta)
  }


keys.table.median = ok_keys_learning %>% group_by(username, key_from, key_to, size_from, size_to) %>% 
  summarise(medianRT = median(RT), sdRT = sd(RT), rateRT = learning_rate(RT))

keys.table.median = keys.table.median %>% arrange(username, medianRT) %>% group_by(username) %>% mutate(rankRT = percent_rank(rateRT), transition= paste(key_from, key_to, sep = ' - '), size_trans = size_from + size_to, devRT = scale(medianRT, scale = F, center = T))

# rank within each subject
plot.median = ggplot(keys.table.median, aes(x = key_from, y = medianRT)) + 
    geom_errorbar(aes(ymin=medianRT-sdRT, ymax=medianRT+sdRT), width=.1) +
    geom_line() + 
    geom_point() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + facet_grid( . ~ username)
print(plot.median)

keys.table.rank = keys.table.median %>% group_by(key_from, key_to, size_from, size_to, transition, size_trans) %>% summarise(meandev = mean(devRT), meanrank = mean(rankRT), medianrank = median(rankRT), count = n(), minrank = min(rankRT), maxrank = max(rankRT)) %>% arrange(meanrank)

keys.table.median = keys.table.median %>% mutate(
         to1 = length(grep("1", key_to)),
         to2 = length(grep("2", key_to)),
         to3 = length(grep("3", key_to)),
         to4 = length(grep("4", key_to)),
         from1 = length(grep("1", key_from)),
         from2 = length(grep("2", key_from)),
         from3 = length(grep("3", key_from)),
         from4 = length(grep("4", key_from))
)

keys.table.rank = subset(keys.table.rank, count > 1)
plot.rank = ggplot(keys.table.median, aes(x = transition, y = rankRT, col = username)) + 
    geom_point() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
#print(plot.rank)
keys.table.median$logmedianrank = logit((keys.table.median$rankRT + 0.1)*0.9)


keys.table.extremes = subset(keys.table.median, size_to != 2 )

model.rank = lmp(rankRT ~ size_to, data = keys.table.extremes, perm = 'Exact')
summary(model.rank)
plot( jitter(rankRT) ~ jitter(size_to), keys.table.extremes)

model.rank = lm(rankRT ~ to1*to2 + to1*to3 + to1*to4 + to2*to3 + to2*to4 + to3*to4, data = keys.table.median)
summary(model.rank)
model.rank = lm(logmedianrank ~ from1 + from2 + from3 + from4, data = keys.table.median)
summary(model.rank)

plot(keys.table.rank$medianrank, lwd = 2, type = "l")
lines(keys.table.rank$minrank, lty = 2)
lines(keys.table.rank$maxrank, lty = 2)

# par(mfrow = c(1, 3))
# boxplot(keys.table.rank$medianrank ~ keys.table.rank$size_trans, main = "transition")
# boxplot(keys.table.rank$medianrank ~ keys.table.rank$size_from, main = "from")
# boxplot(keys.table.rank$medianrank ~ keys.table.rank$size_to, main = "to")
# 
# boxplot(keys.table.rank$medianrank ~ keys.table.rank$to1, main = "to_1")
# 
# plot.keystrokepairs = ggplot(keys.table.rank, aes(x = key_from, y = key_to, fill = medianRT)) + geom_tile() + theme_classic()
# print(plot.keystrokepairs)

```


Same but for sequences

Baseline
```{r}


ok_trials = subset(trials.table, paced == 0 & trial_type != "missing" & accuracy == 1)                                              
# baseline
ok_trials_baseline = subset(ok_trials, sess_num == 1 & trial < 5 )
ok_trials_learning = subset(ok_trials, trial > 5 & trial < 11 & username %in% learners )

trials.table.median = ok_trials_baseline %>% group_by(username, true_sequence) %>% summarise(medianRT = median(RT), sdRT = sd(RT))

trials.table.median = trials.table.median %>% arrange(username, medianRT) %>% group_by(username) %>% mutate(rankRT = percent_rank(medianRT), devRT = scale(medianRT, scale = F, center = T)) %>% mutate(sequence_length = nchar(as.character(true_sequence)))                                                   

# rank within each subject
trials.table.rank = trials.table.median %>% group_by(true_sequence, sequence_length) %>% summarise(meandev = mean(devRT), meanrank = mean(rankRT), medianrank = median(rankRT), count = n(), minrank = min(rankRT), maxrank = max(rankRT)) %>% arrange(meanrank) 

#trials.table.rank = subset(trials.table.rank, count > 1)
plot.rank = ggplot(trials.table.median, aes(x = true_sequence, y = rankRT, col = username)) + 
    geom_point() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
print(plot.rank)

trials.table.rank$logmedianrank = logit(trials.table.rank$medianrank + 0.0001)
#model.rank = lm(logmedianrank ~ size_from + size_to, data = keys.table.rank)
#summary(model.rank)

plot(trials.table.rank$medianrank, lwd = 2, type = "l")
lines(trials.table.rank$minrank, lty = 2)
lines(trials.table.rank$maxrank, lty = 2)

plot(trials.table.rank$count, jitter(trials.table.rank$medianrank))

plot(trials.table.rank$sequence_length, jitter(trials.table.rank$medianrank))

plot(trials.table.median$sequence_length, jitter(trials.table.median$rankRT))
summary(
lm(trials.table.median$sequence_length ~ trials.table.median$rankRT)
)

```

Learning
```{r}
learners = c("kip1s002", "kip1s003", "kip1s004", "kip1s005", "kip1s006", "kip1s008", "kip1s009", "lup0s002")
learners = c("kip1s002", "kip1s003", "kip1s004", "kip1s005", "kip1s008")

ok_trials = subset(trials.table, accuracy == 1 &  paced == 0 & trial_type != 'missed' )

myfunc <- function(alpha, x, y) sum((y - alpha[1]+ alpha[2]*exp(-alpha[3]*x))^2)

learning_rate = function(y, plotit = F, main){ 
  # x = seq(length(y)) - 1
  # alpha = fminsearch(myfunc, c(500, 300, 1), x,  y )$xval
  # 
  # if(plotit){
  #   print(length(y)) 
  #   print(alpha)
  #   plot(x, y, type = "b", pch = 20, main = main)
  #   lines(x, alpha[1]+ alpha[2]*exp(-alpha[3]*x), col = 'red')
  # }
  n = length(y)
  alpha = (y[1]-mean(y[seq(n -5, n)]))/y[1]
  return(alpha)
}


# learning
ok_trials_learning = subset(ok_trials, trial > 10 & username %in% learners & seq_train == 'trained') %>% group_by(username, true_sequence, sess_num) %>% summarise(medianRT = median(RT), sdRT = sd(RT))
ok_trials_learning$username = droplevels(ok_trials_learning$username)

ok_trials_learning$cluster = as.numeric(as.factor(paste(ok_trials_learning$true_sequence, ok_trials_learning$username)))

# fit with stan
stan_data = list(cluster = ok_trials_learning$cluster, x = ok_trials_learning$sess_num, y = ok_trials_learning$medianRT, 
                 Nclus = max(ok_trials_learning$cluster), N = nrow(ok_trials_learning) )
stan_control = list(adapt_delta = 0.9, max_treedepth = 12)

fit = stan(file = "exponential_fit.stan", chains = 4, iter = 3000, warmup = 2000, data = stan_data, control = stan_control)
pairs(fit, pars = c('mu_hyp', 'sigma_hyp'))
traceplot(fit, par = c('mu_hyp', 'sigma_hyp'))

params = summary(fit)$summary[, "mean"]
a = params[grep("a\\[", names(params))]
b = params[grep("b\\[", names(params))]
c = params[grep("c\\[", names(params))]

trials.table.rate = ok_trials_learning %>% group_by(username, true_sequence, cluster) %>% summarise(rateRT = b[cluster[1]])

for(j in unique(ok_trials_learning$cluster)){
  mydata = subset(as.data.frame(ok_trials_learning), cluster == j)
  y = mydata$medianRT
  x = mydata$sess_num
  plot(x, y, pch = 20, cex = 1, main = j)
  lines(x, a[j]*exp(-b[j]*x) + c[j], col = "red")
}

plot(trials.table.rate$username, trials.table.rate$rateRT, las = 2)

trials.table.rank= trials.table.rate %>% arrange(username, true_sequence, rateRT) %>% group_by(username) %>% mutate(rankRT = percent_rank(rateRT), true_sequence = as.character(true_sequence)) %>% mutate(true_sequence = as.factor(true_sequence), sequence_length  = nchar(as.character(true_sequence)), 
n1 = str_count(true_sequence, "1"),
n2 = str_count(true_sequence, "2"),
n3 = str_count(true_sequence, "3"),
n4 = str_count(true_sequence, "4"))

plot(jitter(trials.table.rank$sequence_length), jitter(trials.table.rank$rankRT))

trials.table.ranked = trials.table.rank %>% group_by(true_sequence, sequence_length) %>% summarise(medianrank = median(rankRT), count = n(), minrank = min(rankRT), maxrank = max(rankRT)) %>% arrange(medianrank) 

plot(trials.table.ranked$medianrank, lwd = 2, type = "l")
lines(trials.table.ranked$minrank, lty = 2)
lines(trials.table.ranked$maxrank, lty = 2)

plot(trials.table.ranked$sequence_length, trials.table.ranked$medianrank)

lm (rankRT ~ n1 + n2 + n3 + n4, data = trials.table.rank)
summary(lm (rankRT ~ n1 + n2 + n3 + n4, data = trials.table.rank))
# rank within each subject
```


```{r}

slow = '1 2 3 - 3 4 - 1 - 2 4 - 1 3 4'
fast = '2 3 4 - 1 4 - 3 - 1 2 - 1 3 4'

print(ggplot(subset(ok_trials_learning, true_sequence ==  slow), 
       aes(x = sess_num, y = medianRT, col = username)) + geom_line())

print(ggplot(subset(ok_trials_learning, true_sequence ==  fast), 
       aes(x = sess_num, y = medianRT, col = username)) + geom_line())


plot.rank = ggplot(trials.table.median, aes(x = true_sequence, y = rankRT, col = username)) + 
    geom_point() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
print(plot.rank)
```


```{r}
trials.table = rbind(trials.table1, trials.table2)
memo.table = memo.table1
keys.table = rbind(keys.table1, keys.table2)
```


Analyze memo

```{r fig.width=11, fig.asp=0.8}

# check missed as well
# plot total mistakes

ok_memo = subset(memo.table, accuracy == 1)

plot.RT = ggplot(ok_memo, aes(x = sess_num, y = RT, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ .) + theme(legend.position="right")

plot.attempts = ggplot(memo.table, aes(x = true_sequence, fill = as.factor(seq_train))) + geom_bar() + facet_grid( username ~ sess_num) + theme(axis.text.x = element_text(angle = 90, hjust = 1))

plot.totalRT = ggplot(memo.table %>% group_by(username, sess_num, true_sequence, seq_train) %>% summarise(totalRT = sum(RT)), aes(x = sess_num, y = totalRT, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_point() + geom_line(lwd=1) + facet_grid( username ~ .) + theme(legend.position="right") 



print(plot.RT)
print(plot.attempts)
print(plot.totalRT)

```



Analyze trial times
```{r fig.width=11, fig.asp=0.8}

maxy = 4500 
miny = 500  
ok_trials = subset(trials.table, accuracy == 1)
unpaced_trials = subset(trials.table, paced == 0 & trial_type != "missing")
paced_trials = subset(trials.table, paced == 1 & trial_type != "missing")
ok_unpaced_trials = subset(unpaced_trials, accuracy == 1)
ok_paced_trials = subset(paced_trials, accuracy == 1)
                      
plot.RT = ggplot(ok_unpaced_trials, aes(x = trial, y = RT, col = as.factor(seq_train), group = true_sequence)) + geom_line(lwd=1) + geom_point() + ylim(miny, maxy) + facet_grid( username ~ sess_num) + theme(legend.position="none")
plot.MT = ggplot(ok_unpaced_trials, aes(x = trial, y = MT, col = as.factor(seq_train), group = true_sequence)) + geom_line(lwd=1) + geom_point() + ylim(miny, maxy) + facet_grid( username ~ sess_num) + theme(legend.position="bottom")

plot.RT.paced = ggplot(ok_paced_trials, aes(x = trial, y = RT, col = as.factor(seq_train), group = true_sequence)) + geom_line(lwd=1) + geom_point() + ylim(miny, maxy) + facet_grid( username ~ sess_num) + theme(legend.position="none")
plot.MT.paced = ggplot(ok_paced_trials, aes(x = trial, y = MT, col = as.factor(seq_train), group = true_sequence)) + geom_line(lwd=1) + geom_point() + ylim(miny, maxy) + facet_grid( username ~ sess_num) + theme(legend.position="none")

print(plot.RT)
print(plot.MT)
#print(plot.RT.paced)
print(plot.MT.paced)


```



Mean and variance
```{r fig.width=11, fig.asp=0.8}

last_trials = subset(unpaced_trials, trial > 5 & trial < 11) %>% group_by(username, sess_num, true_sequence, seq_train) %>% summarise(meanMT = mean(MT), sdMT = sd(MT))

plot.meanMT = ggplot(last_trials, aes(x = sess_num, y = meanMT, group = true_sequence, col = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid(username ~ . ) + theme(legend.position="none")

plot.sdMT = ggplot(last_trials, aes(x = sess_num, y = sdMT, group = true_sequence, col = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid(. ~ username ) + theme(legend.position="none")

print(plot.meanMT)
print(plot.sdMT)


# aggregate within user

last_trials.user = last_trials %>% group_by(username, sess_num, seq_train) %>% summarise(meanMT = mean(meanMT), sdMT = mean(sdMT))

plot.meanMT.user = ggplot(last_trials.user, aes(x = sess_num, y = meanMT, col = username, lty = as.factor(seq_train), shape = as.factor(seq_train))) + geom_line(lwd=1) + geom_point(size = 3)

plot.sdMT.user = ggplot(last_trials.user, aes(x = sess_num, y = sdMT, col = username, lty = as.factor(seq_train), shape = as.factor(seq_train))) + geom_line(lwd=1) + geom_point(size = 3)
print(plot.meanMT.user)
print(plot.sdMT.user)



```

Wrong trials 

CONTROL FOR MISSING

```{r fig.width=11, fig.asp=0.8}

unpaced_trials.wrong = unpaced_trials %>% group_by(username, sess_num, true_sequence, seq_train) %>% summarise(wrong = sum(accuracy < 1))
paced_trials.wrong = paced_trials %>% group_by(username, sess_num, true_sequence, seq_train) %>% summarise(wrong = sum(accuracy < 1))

plot.unpaced.wrong = ggplot(unpaced_trials.wrong, aes(x = sess_num, y = wrong, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ .) + theme(legend.position="none")
plot.paced.wrong = ggplot(paced_trials.wrong, aes(x = sess_num, y = wrong, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ .) + theme(legend.position="none")

print(plot.unpaced.wrong)
print(plot.paced.wrong)

```


```{r fig.width=11, fig.asp=0.8}
# plot also group aggregate per sequence and trained versus untrained
finishers = c("kip1s002", "kip1s003", "kip1s004", "kip1s005", "kip1s008", "kip1s009")
ok_unpaced_trials.group = subset(ok_unpaced_trials, username %in% finishers) %>% group_by(trial, sess_num, seq_train) %>% summarise(MT = mean(MT))

plot.MT.group = ggplot(ok_unpaced_trials.group, aes(x = trial, y = MT, col = as.factor(seq_train), group =  as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( . ~ sess_num) + theme(legend.position="bottom")

print(plot.MT.group)

ok_unpaced_trials.group = subset(ok_unpaced_trials, username %in% finishers & trial > 5 & trial < 11 ) %>% group_by(sess_num, seq_train) %>% summarise(MT = mean(MT))

plot.MT.group = ggplot(ok_unpaced_trials.group, aes(x = sess_num, y = MT, col = as.factor(seq_train), group =  as.factor(seq_train))) + geom_line(lwd=1) + geom_point(size = 2)

print(plot.MT.group)

```





```{r}
# paced_trials$diff.exec_fix = paced_trials$clock_execution  - paced_trials$clock_fixation
# paced_trials$diff.feed_exec = paced_trials$clock_feedback  - paced_trials$clock_execution 
# 
# hist(paced_trials$diff.exec_fix, 50)
# hist(paced_trials$diff.feed_exec, 50)

```

Analyze duration


```{r fig.width=11, fig.asp=0.8}
plot.duration = ggplot(trials.table, aes(x = sess_num, y = global_clock/60, col = username, group = username)) + 
  stat_summary(fun.y = max, geom = "line", lwd = 1) +  stat_summary(fun.y = max, geom = "point") + ylab("Session duration")

print(plot.duration)

```


Analyze dates and times


```{r fig.width=11, fig.asp=0.8}

trials.times = trials.table %>% mutate(sess_date = as.Date(sess_date), sess_time = as.POSIXct(sess_time, format="%H:%M:%S")) %>% group_by(username, sess_num, sess_date, sess_time, sess_type) %>% sample_n(1) 
#kip1 = grep('kip1', trials.times$username)
#trials.times =trials.times[kip1, ]
plot.dates = ggplot(trials.times, aes(x = sess_num, y = sess_date, col = username, group = username)) + geom_line() + geom_point() + xlab("Session number") + ylab("Session date") + scale_y_date()

print(plot.dates)

table(trials.times$username)

plot.times = ggplot(trials.times, aes(x = sess_num, y = sess_time)) + geom_line() + geom_point() + xlab("Session number") + ylab("Session time") + facet_grid( . ~ username)
print(plot.times)

```




Analyze clocks

```{r}

trialsfile = paste0('../data/trialsfile-lup0s002_fmri.csv')
trials.table = read.table(trialsfile, sep =';', header = T, quote = "")
paced_trials = subset(trials.table, paced == 1)
           
diff.1 = apply(paced_trials[c("clock_fixation", "clock_execution", "clock_feedback", "clock_finished")], 2, diff)           
diff.2 = apply(paced_trials[c("clock_fixation", "clock_execution", "clock_feedback", "clock_finished")], 1, diff) 
#print(diff.1)
#print(diff.2)
#plot.fixation = ggplot(paced_trials, aes(x = trial, y = clock_fixation, group = sess_num, col = sess_num, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ true_sequence ) + theme(legend.position="none")

#print(plot.fixation)

```



Lund pilot
```{r fig.width=11, fig.asp=0.8}
plot.MT = ggplot(subset(ok_unpaced_trials, username == "lup0s002"), aes(x = trial, y = MT, col = as.factor(true_sequence), group = true_sequence)) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ sess_num) + theme(legend.position="bottom")

last_trials = subset(ok_unpaced_trials, username == "lup0s002" & trial > 15) %>% group_by(sess_num, true_sequence, seq_train) %>% summarise(meanMT = mean(MT), sdMT = sd(MT))

plot.meanMT = ggplot(last_trials, aes(x = sess_num, y = meanMT, group = true_sequence, col = as.factor(seq_train))) + geom_line(lwd=1) + geom_point(size=2) + theme(legend.position="none")

last_trials = subset(ok_unpaced_trials, username == "lup0s002" & trial > 15) %>% group_by(sess_num, seq_train) %>% summarise(meanMT = mean(MT), sdMT = sd(MT))

plot.meanMT2 = ggplot(last_trials, aes(x = sess_num, y = meanMT, col = as.factor(seq_train))) + geom_line(lwd=1) + geom_point(size=2) + theme(legend.position="none")

print(plot.MT)
print(plot.meanMT)
print(plot.meanMT2)

```

```{r fig.width=11, fig.asp=0.8}

ok_trials = subset(trials.table, accuracy == 1 &  paced == 0)
unpaced_trials = subset(trials.table, paced == 0)
paced_trials = subset(trials.table, paced == 1 & accuracy == 1)
                      
plot.RT = ggplot(ok_trials, aes(x = trial, y = RT, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ sess_num + paced) + theme(legend.position="none")
plot.MT = ggplot(ok_trials, aes(x = trial, y = MT, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ sess_num ) + theme(legend.position="none")
plot.acc = ggplot(unpaced_trials, aes(x = trial, y = accuracy, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ sess_num) + theme(legend.position="none")

print(plot.RT)
print(plot.MT)
print(plot.acc)

```


```{r}
#trialsfile = paste0('../../SeqLearnPilot/dataLundPilot/trialsfile-lup0s002_fmri.csv')
#trials.table = read.table(trialsfile, sep =';', header = T, quote = "")
#ok_trials = subset(trials.table, accuracy == 1 & run > 1)
#table(ok_trials$true_sequence)
#table(ok_trials$seq_train)

```

