---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
Questions: 
how does savings relate to learning

look at baseline and learning
analyze the number of errors

Conclusions
- use new untrained sequences every time
- considerable transfer
- some train twice the same day or skip several days. Make it clear that we will catch them 
- longer from and to chords are more difficult: maximize 2 - 3  and 3 - 2 chords, and 2 - 3 over 3 - 2 
- unseen and untrained take the  same time: memorization does not make a difference


```{r}
rm(list=ls())
library(ggplot2)
library(reshape2)
library(dplyr)
library(GGally)
library(network)
library(boot)
setwd("~/projects/SeqLearn/stats")

suffix = '20181205_1940-KIpilot1db'
keysfile = paste0('../data/archive/keys_table-', suffix, '.csv')
trialsfile = paste0('../data/archive/trials_table-', suffix, '.csv')
memofile = paste0('../data/archive/memo_table-', suffix, '.csv')

suffix0 = '20181126_2119-KIpilot0db'
keysfile0 = paste0('../data/archive/keys_table-', suffix0, '.csv')
trialsfile0 = paste0('../data/archive/trials_table-', suffix0, '.csv')
memofile0 = paste0('../data/archive/memo_table-', suffix0, '.csv')

suffix2 = '20181206_0820-LundfMRIpilot0db'
keysfile2 = paste0('../data/archive/keys_table-', suffix2, '.csv')
trialsfile2 = paste0('../data/archive/trials_table-', suffix2, '.csv')

keys.table1 = unique(read.table(keysfile, sep =';', header = T, quote = "")[-1])
keys.table1 = subset(keys.table1, !(username == 'kip1s006' & sess_num == 15))
trials.table1 = unique(read.table(trialsfile, sep =';', header = T,quote = "")[-1])
trials.table1 = subset(trials.table1, !(username == 'kip1s006' & sess_num == 15))
memo.table1 = unique(read.table(memofile, sep =';', header = T,quote = "")[-1])
memo.table1 = subset(memo.table1, !(username == 'kip1s006' & sess_num == 15))

keys.table2 = unique(read.table(keysfile2, sep =';', header = T, quote = "")[-1])
trials.table2 = unique(read.table(trialsfile2, sep =';', header = T,quote = "")[-1])

# remove some data 

trials.table0 = unique(read.table(trialsfile0, sep =';', header = T,quote = "")[-1])
trials.table0 = subset(trials.table0, username != 'kip0s001')
trials.table = rbind(trials.table1, trials.table0, trials.table2)

keys.table0 = unique(read.table(keysfile0, sep =';', header = T,quote = "")[-1])
keys.table0 = subset(keys.table0, username != 'kip0s001')
keys.table = rbind(keys.table1, keys.table0, keys.table2)

memo.table0 = unique(read.table(memofile0, sep =';', header = T,quote = "")[-1])
memo.table0 = subset(memo.table0, username != 'kip0s001')
memo.table = rbind(memo.table1, memo.table0)
#keys.melt = melt(keys.table, id.vars = c("cumulative_trial","trial","keystroke","response") )
#trials.melt = melt(keys.table, id.vars = c("cumulative_trial","trial","keystroke","response") )

```
Analyze chords

```{r fig.width=11, fig.asp=0.8}

hasx = function(string, x){grep(, x)}

ok_keys = subset(keys.table, paced == 0 & trial_type != "missing" & accuracy == 1 & keystroke > 0) %>%
  mutate(size_from = nchar(gsub(" ", "", key_from)), 
         size_to = nchar(gsub(" ", "", key_to)))

# baseline
ok_keys_baseline = subset(ok_keys, sess_num == 1 & trial < 5 )
keys.table.median = ok_keys_baseline %>% group_by(username, key_from, key_to, size_from, size_to) %>% summarise(medianRT = median(RT), sdRT = sd(RT))
keys.table.median = keys.table.median %>% arrange(username, medianRT) %>% group_by(username) %>% mutate(rankRT = percent_rank(medianRT), transition= paste(key_from, key_to, sep = ' - '), size_trans = size_from + size_to, devRT = scale(medianRT, scale = F, center = T))

# rank within each subject
plot.median = ggplot(keys.table.median, aes(x = key_from, y = medianRT)) + 
    geom_errorbar(aes(ymin=medianRT-sdRT, ymax=medianRT+sdRT), width=.1) +
    geom_line() + 
    geom_point() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + facet_grid( . ~ username)
print(plot.median)

keys.table.rank = keys.table.median %>% group_by(key_from, key_to, size_from, size_to, transition, size_trans) %>% summarise(meandev = mean(devRT), meanrank = mean(rankRT), medianrank = median(rankRT), count = n(), minrank = min(rankRT), maxrank = max(rankRT)) %>% arrange(meanrank)

keys.table.rank = keys.table.rank %>% mutate(
         to1 = length(grep("1", key_to)),
         to2 = length(grep("2", key_to)),
         to3 = length(grep("3", key_to)),
         to4 = length(grep("4", key_to))
)

keys.table.rank = subset(keys.table.rank, count > 1)
plot.rank = ggplot(keys.table.median, aes(x = transition, y = rankRT, col = username)) + 
    geom_point() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
#print(plot.rank)
keys.table.rank$logmedianrank = logit(keys.table.rank$medianrank + 0.0001)
model.rank = lm(logmedianrank ~ size_from + size_to, data = keys.table.rank)
summary(model.rank)
model.rank = lm(logmedianrank ~ to1 + to2 + to3 + to4, data = keys.table.rank)
summary(model.rank)

plot(keys.table.rank$medianrank, lwd = 2, type = "l")
lines(keys.table.rank$minrank, lty = 2)
lines(keys.table.rank$maxrank, lty = 2)

par(mfrow = c(1, 3))
boxplot(keys.table.rank$medianrank ~ keys.table.rank$size_trans, main = "transition")
boxplot(keys.table.rank$medianrank ~ keys.table.rank$size_from, main = "from")
boxplot(keys.table.rank$medianrank ~ keys.table.rank$size_to, main = "to")

boxplot(keys.table.rank$medianrank ~ keys.table.rank$to1, main = "to_1")

# plot.keystrokepairs = ggplot(keys.table.rank, aes(x = key_from, y = key_to, fill = medianRT)) + geom_tile() + theme_classic()
# print(plot.keystrokepairs)

```

```{r}
trials.table = rbind(trials.table1, trials.table2)
memo.table = memo.table1
keys.table = rbind(keys.table1, keys.table2)
```


Analyze memo

```{r fig.width=11, fig.asp=0.8}

# check missed as well
# plot total mistakes

ok_memo = subset(memo.table, accuracy == 1)

plot.RT = ggplot(ok_memo, aes(x = sess_num, y = RT, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ .) + theme(legend.position="right")

plot.attempts = ggplot(memo.table, aes(x = true_sequence, fill = as.factor(seq_train))) + geom_bar() + facet_grid( username ~ sess_num) + theme(axis.text.x = element_text(angle = 90, hjust = 1))

plot.totalRT = ggplot(memo.table %>% group_by(username, sess_num, true_sequence, seq_train) %>% summarise(totalRT = sum(RT)), aes(x = sess_num, y = totalRT, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_point() + geom_line(lwd=1) + facet_grid( username ~ .) + theme(legend.position="right") 



print(plot.RT)
print(plot.attempts)
print(plot.totalRT)

```



Analyze trial times
```{r fig.width=11, fig.asp=0.8}

maxy = 4500 
miny = 500  
ok_trials = subset(trials.table, accuracy == 1)
unpaced_trials = subset(trials.table, paced == 0 & trial_type != "missing")
paced_trials = subset(trials.table, paced == 1 & trial_type != "missing")
ok_unpaced_trials = subset(unpaced_trials, accuracy == 1)
ok_paced_trials = subset(paced_trials, accuracy == 1)
                      
plot.RT = ggplot(ok_unpaced_trials, aes(x = trial, y = RT, col = as.factor(seq_train), group = true_sequence)) + geom_line(lwd=1) + geom_point() + ylim(miny, maxy) + facet_grid( username ~ sess_num) + theme(legend.position="none")
plot.MT = ggplot(ok_unpaced_trials, aes(x = trial, y = MT, col = as.factor(seq_train), group = true_sequence)) + geom_line(lwd=1) + geom_point() + ylim(miny, maxy) + facet_grid( username ~ sess_num) + theme(legend.position="bottom")

plot.RT.paced = ggplot(ok_paced_trials, aes(x = trial, y = RT, col = as.factor(seq_train), group = true_sequence)) + geom_line(lwd=1) + geom_point() + ylim(miny, maxy) + facet_grid( username ~ sess_num) + theme(legend.position="none")
plot.MT.paced = ggplot(ok_paced_trials, aes(x = trial, y = MT, col = as.factor(seq_train), group = true_sequence)) + geom_line(lwd=1) + geom_point() + ylim(miny, maxy) + facet_grid( username ~ sess_num) + theme(legend.position="none")

print(plot.RT)
print(plot.MT)
#print(plot.RT.paced)
print(plot.MT.paced)


```



Mean and variance
```{r fig.width=11, fig.asp=0.8}

last_trials = subset(unpaced_trials, trial > 5 & trial < 11) %>% group_by(username, sess_num, true_sequence, seq_train) %>% summarise(meanMT = mean(MT), sdMT = sd(MT))

plot.meanMT = ggplot(last_trials, aes(x = sess_num, y = meanMT, group = true_sequence, col = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid(username ~ . ) + theme(legend.position="none")

plot.sdMT = ggplot(last_trials, aes(x = sess_num, y = sdMT, group = true_sequence, col = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid(. ~ username ) + theme(legend.position="none")

print(plot.meanMT)
print(plot.sdMT)


# aggregate within user

last_trials.user = last_trials %>% group_by(username, sess_num, seq_train) %>% summarise(meanMT = mean(meanMT), sdMT = mean(sdMT))

plot.meanMT.user = ggplot(last_trials.user, aes(x = sess_num, y = meanMT, col = username, lty = as.factor(seq_train), shape = as.factor(seq_train))) + geom_line(lwd=1) + geom_point(size = 3)

plot.sdMT.user = ggplot(last_trials.user, aes(x = sess_num, y = sdMT, col = username, lty = as.factor(seq_train), shape = as.factor(seq_train))) + geom_line(lwd=1) + geom_point(size = 3)
print(plot.meanMT.user)
print(plot.sdMT.user)



```

Wrong trials 

CONTROL FOR MISSING

```{r fig.width=11, fig.asp=0.8}

unpaced_trials.wrong = unpaced_trials %>% group_by(username, sess_num, true_sequence, seq_train) %>% summarise(wrong = sum(accuracy < 1))
paced_trials.wrong = paced_trials %>% group_by(username, sess_num, true_sequence, seq_train) %>% summarise(wrong = sum(accuracy < 1))

plot.unpaced.wrong = ggplot(unpaced_trials.wrong, aes(x = sess_num, y = wrong, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ .) + theme(legend.position="none")
plot.paced.wrong = ggplot(paced_trials.wrong, aes(x = sess_num, y = wrong, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ .) + theme(legend.position="none")

print(plot.unpaced.wrong)
print(plot.paced.wrong)

```


```{r fig.width=11, fig.asp=0.8}
# plot also group aggregate per sequence and trained versus untrained
finishers = c("kip1s002", "kip1s003", "kip1s004", "kip1s005", "kip1s008")
ok_unpaced_trials.group = subset(ok_unpaced_trials, username %in% finishers) %>% group_by(trial, sess_num, seq_train) %>% summarise(MT = mean(MT))

plot.MT.group = ggplot(ok_unpaced_trials.group, aes(x = trial, y = MT, col = as.factor(seq_train), group =  as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( . ~ sess_num) + theme(legend.position="bottom")

print(plot.MT.group)

ok_unpaced_trials.group = subset(ok_unpaced_trials, username %in% finishers & trial > 5 & trial < 11 ) %>% group_by(sess_num, seq_train) %>% summarise(MT = mean(MT))

plot.MT.group = ggplot(ok_unpaced_trials.group, aes(x = sess_num, y = MT, col = as.factor(seq_train), group =  as.factor(seq_train))) + geom_line(lwd=1) + geom_point(size = 2)

print(plot.MT.group)

```





```{r}
# paced_trials$diff.exec_fix = paced_trials$clock_execution  - paced_trials$clock_fixation
# paced_trials$diff.feed_exec = paced_trials$clock_feedback  - paced_trials$clock_execution 
# 
# hist(paced_trials$diff.exec_fix, 50)
# hist(paced_trials$diff.feed_exec, 50)

```

Analyze duration


```{r fig.width=11, fig.asp=0.8}
plot.duration = ggplot(trials.table, aes(x = sess_num, y = global_clock/60, col = username, group = username)) + 
  stat_summary(fun.y = max, geom = "line", lwd = 1) +  stat_summary(fun.y = max, geom = "point") + ylab("Session duration")

print(plot.duration)

```


Analyze dates and times


```{r fig.width=11, fig.asp=0.8}

trials.times = trials.table %>% mutate(sess_date = as.Date(sess_date), sess_time = as.POSIXct(sess_time, format="%H:%M:%S")) %>% group_by(username, sess_num, sess_date, sess_time, sess_type) %>% sample_n(1) 
#kip1 = grep('kip1', trials.times$username)
#trials.times =trials.times[kip1, ]
plot.dates = ggplot(trials.times, aes(x = sess_num, y = sess_date, col = username, group = username)) + geom_line() + geom_point() + xlab("Session number") + ylab("Session date") + scale_y_date()

print(plot.dates)

table(trials.times$username)

plot.times = ggplot(trials.times, aes(x = sess_num, y = sess_time)) + geom_line() + geom_point() + xlab("Session number") + ylab("Session time") + facet_grid( . ~ username)
print(plot.times)

```




Analyze clocks

```{r}

trialsfile = paste0('../data/trialsfile-lup0s002_fmri.csv')
trials.table = read.table(trialsfile, sep =';', header = T, quote = "")
paced_trials = subset(trials.table, paced == 1)
           
diff.1 = apply(paced_trials[c("clock_fixation", "clock_execution", "clock_feedback", "clock_finished")], 2, diff)           
diff.2 = apply(paced_trials[c("clock_fixation", "clock_execution", "clock_feedback", "clock_finished")], 1, diff) 
print(diff.1)
print(diff.2)
#plot.fixation = ggplot(paced_trials, aes(x = trial, y = clock_fixation, group = sess_num, col = sess_num, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ true_sequence ) + theme(legend.position="none")

#print(plot.fixation)

```



Lund pilot
```{r fig.width=11, fig.asp=0.8}
plot.MT = ggplot(subset(ok_unpaced_trials, username == "lup0s002"), aes(x = trial, y = MT, col = as.factor(true_sequence), group = true_sequence)) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ sess_num) + theme(legend.position="bottom")

print(plot.MT)

```

```{r fig.width=11, fig.asp=0.8}

ok_trials = subset(trials.table, accuracy == 1 &  paced == 0)
unpaced_trials = subset(trials.table, paced == 0)
paced_trials = subset(trials.table, paced == 1 & accuracy == 1)
                      
plot.RT = ggplot(ok_trials, aes(x = trial, y = RT, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ sess_num + paced) + theme(legend.position="none")
plot.MT = ggplot(ok_trials, aes(x = trial, y = MT, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ sess_num ) + theme(legend.position="none")
plot.acc = ggplot(unpaced_trials, aes(x = trial, y = accuracy, col = true_sequence, group = true_sequence, lty = as.factor(seq_train))) + geom_line(lwd=1) + geom_point() + facet_grid( username ~ sess_num) + theme(legend.position="none")

print(plot.RT)
print(plot.MT)
print(plot.acc)

```