---
title: "R Notebook"
output: html_notebook
---

Untrained are mirrored and shifted
What do I need to know?

Try sequences with different distances between chords. 
What is the effect of distance in performance and in learning?
Is there a difference in learning when chords are repeated with different transitions, compared to learning new chords?


Study timing
```{r}
rm(list=ls())
library(reshape)
library(sna)
library(igraph)
library(proxy)
library(rjson)

source("./SequenceStructureFuncs.R")
output_prefix = '//aldrecentrum.local/rf/benjamin.garzon/My Documents/Projects/SeqLearn/scheduling/sequences/sequences_lue1_'

```

```{r}
# define alphabet

chords = rbind(
  c(1, 1, 1, 0),
#  c(1, 1, 0, 1),
#  c(1, 0, 1, 1),
  c(0, 1, 1, 1), 
  c(1, 1, 0, 0),
  c(0, 0, 1, 1),
  c(1, 0, 1, 0),
  c(0, 1, 0, 1),
  c(1, 0, 0, 1),
  c(0, 1, 1, 0),
  c(1, 0, 0, 0),
  c(0, 1, 0, 0),
  c(0, 0, 1, 0),
  c(0, 0, 0, 1),
  c(1, 1, 1, 1)
)             


chords.1 = rbind(
  c(1, 1, 1, 0),
  c(1, 1, 0, 1),
  c(1, 1, 0, 0),
  c(0, 1, 0, 1)
)             


chords.2 = rbind(
  c(0, 1, 1, 1), 
  c(1, 0, 1, 1),
  c(0, 0, 1, 1),
  c(1, 0, 1, 0)
)             


```


Path generation

```{r}
# generate all paths
seq_size = 5

paths = generate_paths(chords, allowed_dist = c(3), seq_size)
# select the most relevant paths
chunks = select_unique(paths, seq_size)
```

Configuration 1:
Untrained and trained have common chords but different transitions. Transitions involve 3 fingers always.


```{r}
nchords = nrow(chords)

maxdist.vec = 2*(seq_size - 1)

# compute distances
# hamming distance considering transitions
vecdist = get_vecdist(chunks, nchords)

# number of different elements
eldist = proxy::dist(chunks, chunkdist)

vecdist.mat = as.matrix(vecdist)
eldist.mat = as.matrix(eldist)
```

Find clusters
```{r}

schedule_size = 3 # number of trained

#  find clusters of sequences with uncommon transitions
hc.complete = hclust(maxdist.vec - vecdist, method = "complete")
plot(hc.complete)
clusters = cutree(hc.complete, h = 1)
clusters.table = table(clusters)
sel.clus = which(clusters.table > 8 )# at least 8 different sequences needed
#sel.clus = which(clusters.table > max(clusters.table) - 4)

sel.chunks =  list() 
degree = min.eldist = NULL
myfinger_distance = mychord_distance = myschedules = mytransitions = NULL
for (i in seq(length(sel.clus))){
  sel.chunks[[i]] = chunks[which(clusters == sel.clus[i])]
  chunks.vecdist = get_vecdist(sel.chunks[[i]], nchords)
  chunks.eldist = proxy::dist(sel.chunks[[i]], chunkdist)
  schedules = get_schedules_complete(sel.chunks[[i]], schedule_size) # contains possible configurations of trained and untrained sequences
  myfinger_distance = c(myfinger_distance,
                        sapply(schedules, finger_distribution_distance, chords)
  )
  mychord_distance = c(mychord_distance,
                       sapply(schedules, chord_distance, size = schedule_size)
  )
  myschedules = c(myschedules, 
                 schedules)
  mytransitions = rbind(mytransitions, 
                 t(sapply(schedules, get_transition_distribution, nchords)))
  print(i)
}

# ensure that the frequency of fingers is the same and that there are the minimum possible number of common chords between trained and untrained

plot(jitter(mychord_distance), jitter(myfinger_distance), pch = 20, cex = 0.3) 

chosen_indices = which(mychord_distance == max(mychord_distance))
chosen_schedules.1 = myschedules[chosen_indices]
myfinger_distance = myfinger_distance[chosen_indices]

chosen_schedules.2 = chosen_schedules.1[order(myfinger_distance)]

# check distribution of fingers and transitions
```

# write out
```{r}
chosen_schedules = chosen_schedules.2[c(2 , 3)] # arbitrary

vecs.trained = vecs.untrained = NULL

for (i in seq(length(chosen_schedules))){
  
  schedule = chosen_schedules[[i]]
    
  print("----")
  print(i)
  print("Trained:")
  print(schedule$trained)
  finger_distribution.trained = sapply(schedule$trained, get_finger_distribution, chords)
  finger_distribution.untrained = sapply(schedule$untrained, get_finger_distribution, chords)  
  vecs.trained = rbind(vecs.trained, rowSums(sapply(schedule$trained, chunk_to_bin, nchords)))
  vecs.untrained = rbind(vecs.untrained, rowSums(sapply(schedule$untrained, chunk_to_bin, nchords)))

  transition.distribution = get_transition_distribution(schedule, nchords)
  print("Finger distribution")
  print(t(finger_distribution.trained))
  print(t(finger_distribution.untrained))
  print("Finger distribution distance")
  print(sapply(list(schedule), finger_distribution_distance, chords))
  print("Chord distance")
  print(sapply(list(schedule), chord_distance, size = schedule_size))  
}
```


```{r}
# if I select k schedules, how many different transitions do I cover?
k = 2
n_chosen = length(chosen_schedules)
mycomb = combn(n_chosen, k)
for (j in seq(ncol(mycomb))){
  
  s = table(
  12/k*colSums(vecs.trained[mycomb[, j], ])
  )
  print(mycomb[, j])
  print(s)
  }

#chosen_schedules = chosen_schedules[c(1, 3)]
```


```{r}
set.seed(4) # to permutate the sequences
permutations = NULL
permutations[[1]] = c(4, 1, 5, 2, 3, 6)
permutations[[2]] = c(1, 4, 2, 5, 3, 6)

for (i in seq(length(chosen_schedules))){
  
  schedule = chosen_schedules[[i]]
  print(i)
  finger_distribution.trained = sapply(schedule$trained, get_finger_distribution, chords)
  finger_distribution.untrained = sapply(schedule$untrained, get_finger_distribution, chords)  
  vecs.trained = rbind(vecs.trained, rowSums(sapply(schedule$trained, chunk_to_bin, nchords)))
  vecs.untrained = rbind(vecs.untrained, rowSums(sapply(schedule$untrained, chunk_to_bin, nchords)))

  transition.distribution = get_transition_distribution(schedule, nchords)
  
  print(t(finger_distribution.trained))
  print(t(finger_distribution.untrained))
  
  json_file = paste0(output_prefix, formatC(i, width = 3, flag = 0), '.json')
  trained.chunks = schedule$trained
  untrained.chunks = schedule$untrained
  #trained = sample(translate_seqs(trained.chunks, chords))
  #untrained = sample(translate_seqs(untrained.chunks, chords))
  trained = sample(translate_seqs(trained.chunks, chords))
  untrained = translate_seqs(untrained.chunks, chords)[permutations[[i]]]
  myjson = toJSON(list(type1 = list(trained = trained, untrained = untrained)))
  print(untrained)
  write(myjson, json_file)
  
} 

```
