---
title: "R Notebook"
output: html_notebook
---

Untrained are mirrored and shifted
What do I need to know?

Try sequences with different distances between chords. 
What is the effect of distance in performance and in learning?
Is there a difference in learning when chords are repeated with different transitions, compared to learning new chords?


Study timing
```{r}
rm(list=ls())
library(reshape)
library(sna)
library(igraph)
library(proxy)
library(rjson)

source("./SequenceStructureFuncs.R")

```

```{r}
# define alphabet

chords = rbind(
  c(1, 1, 1, 0),
  c(1, 1, 0, 1),
  c(1, 0, 1, 1),
  c(0, 1, 1, 1), 
  c(1, 1, 0, 0),
  c(0, 0, 1, 1),
  c(1, 0, 1, 0),
  c(0, 1, 0, 1),
  c(1, 0, 0, 1),
  c(0, 1, 1, 0),
  c(1, 0, 0, 0),
  c(0, 1, 0, 0),
  c(0, 0, 1, 0),
  c(0, 0, 0, 1)
)             


chords.1 = rbind(
  c(1, 1, 1, 0),
  c(1, 1, 0, 1),
  c(1, 1, 0, 0),
  c(0, 1, 0, 1)
)             


chords.2 = rbind(
  c(0, 1, 1, 1), 
  c(1, 0, 1, 1),
  c(0, 0, 1, 1),
  c(1, 0, 1, 0)
)             


```


Path generation

```{r}
# generate all paths
seq_size = 5

paths = generate_paths(chords, c(3), seq_size)
# select the most relevant paths
chunks = select_unique(paths, seq_size)

```

Configuration 1:
Untrained and trained have common chords but different transitions. Transitions involve 3 fingers always.


```{r}
nchords = nrow(chords)

maxdist.vec = 2*(seq_size - 1)

# compute distances
# hamming distance considering transitions
vecdist = get_vecdist(chunks, nchords)

# number of different elements
eldist = proxy::dist(chunks, chunkdist)

vecdist.mat = as.matrix(vecdist)
eldist.mat = as.matrix(eldist)
```

Find clusters
```{r}

schedule_size = 3

#  find clusters of sequences with uncommon transitions
hc.complete = hclust(maxdist.vec - vecdist, method = "complete")
plot(hc.complete)
clusters = cutree(hc.complete, h = 1)
clusters.table = table(clusters)
sel.clus = which(clusters.table > schedule_size*2)# at least 6 different sequences needed

sel.chunks =  list()
degree = min.eldist = NULL
myfinger_distance = mychord_distance = myschedules = mytransitions = NULL
for (i in seq(length(sel.clus))){
  sel.chunks[[i]] = chunks[which(clusters == sel.clus[i])]
  chunks.vecdist = get_vecdist(sel.chunks[[i]], nchords)
  chunks.eldist = proxy::dist(sel.chunks[[i]], chunkdist)
  schedules = get_schedules(sel.chunks[[i]], schedule_size)
  myfinger_distance = c(myfinger_distance,
                        sapply(schedules, finger_distribution_distance, chords)
  )
  mychord_distance = c(mychord_distance,
                       sapply(schedules, chord_distance)
  )
  myschedules =c(myschedules, 
                 schedules)
  mytransitions = rbind(mytransitions, 
                 t(sapply(schedules, get_transition_distribution, nchords)))
                 
  print(i)
  # min.eldist[i] = min(chunks.eldist)
  # if(min(chunks.eldist)==2)
  # hc.el = hclust(chunks.eldist, method = "complete")
  # plot(hc.el)
}

# ensure that the frequency of fingers is the same and that there are the minimum possible number of common chords between trained and untrained

plot(jitter(mychord_distance), jitter(myfinger_distance), pch = 20, cex = 0.3 ) 
chosen_indices = which(myfinger_distance == 0 & mychord_distance==max(mychord_distance))
chosen_schedules = myschedules[chosen_indices]

# check distribution of fingers and transitions
```

# schedules (1 and 2) and (3 and 4) are the same
# write out
```{r}

vecs.trained = vecs.untrained = NULL

for (i in seq(length(chosen_schedules))){
  
  schedule = chosen_schedules[[i]]
    
  print(i)
  finger_distribution.trained = sapply(schedule$trained, get_finger_distribution, chords)
  finger_distribution.untrained = sapply(schedule$untrained, get_finger_distribution, chords)  
  vecs.trained = rbind(vecs.trained, rowSums(sapply(schedule$trained, chunk_to_bin, nchords)))
  vecs.untrained = rbind(vecs.untrained, rowSums(sapply(schedule$untrained, chunk_to_bin, nchords)))

  transition.distribution = get_transition_distribution(schedule, nchords)
  
  print(t(finger_distribution.trained))
  print(t(finger_distribution.untrained))
  
} 


# if I select k schedules, how many different transitions do I cover?
k = 4
n_chosen = length(chosen_schedules)
mycomb = combn(n_chosen, k)
for (j in seq(ncol(mycomb))){
  
  s = table(
  12/k*colSums(vecs.trained[mycomb[, j], ])
  )
  print(mycomb[, j])
  print(s)
  }

chosen_schedules = chosen_schedules[c(1, 3)]

for (i in seq(length(chosen_schedules))){
  
  schedule = chosen_schedules[[i]]
    
  print(i)
  finger_distribution.trained = sapply(schedule$trained, get_finger_distribution, chords)
  finger_distribution.untrained = sapply(schedule$untrained, get_finger_distribution, chords)  
  vecs.trained = rbind(vecs.trained, rowSums(sapply(schedule$trained, chunk_to_bin, nchords)))
  vecs.untrained = rbind(vecs.untrained, rowSums(sapply(schedule$untrained, chunk_to_bin, nchords)))

  transition.distribution = get_transition_distribution(schedule, nchords)
  
  print(t(finger_distribution.trained))
  print(t(finger_distribution.untrained))
  
  json_file = paste0('../scheduling/sequences/sequences_grouped_', formatC(i, width = 3, flag = 0), '.json')
  trained.chunks = schedule$trained
  untrained.chunks = schedule$untrained
  trained = translate_seqs(trained.chunks, chords)
  untrained = translate_seqs(untrained.chunks, chords)
#  myjson = toJSON(list(type1 = c(trained, untrained)))
  myjson = toJSON(list(type1 = list(trained = trained, untrained = untrained)))
  
  write(myjson, json_file)
  
} 



# sel.chunk = sel.chunks[[ 58 ]]
# 
# # observe clustering
# sel.dist = proxy::dist(sel.chunk, chunkdist)
# hc.sel = hclust(sel.dist, method = "single")
# plot(hc.sel)
# 
# trained.chunks = sel.cluster[c(1, 8, 5)]
# untrained.chunks = sel.cluster[c(9, 4, 6)]
# 
# vecdist.results = get_vecdist(c(trained.chunks, untrained.chunks), nchords)
# eldist.results = proxy::dist(c(trained.chunks, untrained.chunks), chunkdist)
# 
# print(as.matrix(vecdist.results))
# print(as.matrix(eldist.results))

# run SeqGen.py to generate schedule
# python SeqGen.py --sequence_file=scheduling\sequences_001.json --schedule_file=scheduling\schedule001
```

```{r}

```



Configuration 1:
Untrained and trained have different chords (and different transitions). Distance between consecutive chords is always 3.

Confirm

```{r}

# trained.dist = get_vecdist(trained.cluster, nchords)
# untrained.dist = get_vecdist(untrained.cluster, nchords)
# hc = hclust(untrained.dist, method = "single")
# plot(hc)
# 
# hc.complete = hclust(as.dist(eldist.mat[sel.chunks, sel.chunks]), method = "single")
# hc.inverse = hclust(as.dist(seq_size - eldist.mat[sel.chunks, sel.chunks]), method = "single")
# plot(hc.single)
# plot(hc.complete)
# clusters.2 = cutree(hc.complete, h = 4)
# mychunks = chunks[as.numeric(names(which(clusters.2==1)))]
# 
# 
# eldist.deg0 = colSums(eldist.mat == 0)
# eldist.deg1 = colSums(eldist.mat == seq_size)
# 
# vecdist.deg = colSums(vecdist.mat == maxdist.vec)
# maxdist = eldist.deg == max(eldist.deg)
# 
# eldist.max = eldist.mat[maxdist, maxdist]
# vecdist.max = vecdist.mat[maxdist, maxdist]
# 
# 
# # disjoint are sequences with distance seq_size -1
# 
# eldist.adj = 1*(eldist.mat == 0)
# eldist.adj = 1*(as.matrix(sel.dist) == 5)
# 
# mygraph.el = graph_from_adjacency_matrix(eldist.adj, mode = "undirected")
# modules.el = edge.betweenness.community(mygraph.el)
# modules.el = fastgreedy.community(mygraph.el)
# modules.el = walktrap.community(mygraph.el)
# modules.el = leading.eigenvector.community(mygraph.el)
# mod.table = table(modules.el$membership)
# sel.mod = which(mod.table == max(mod.table))[1]
# sel.chunks = chunks[modules.el$membership == sel.mod]
# 
# eldist.mod = eldist.mat[modules.el$membership == sel.mod, modules.el$membership == sel.mod]
# vecdist.mod = vecdist.mat[modules.el$membership == sel.mod, modules.el$membership == sel.mod]
# 
# plot(mygraph.el)
# vecdist.adj = 1*(vecdist.mat == maxdist.vec)
# mygraph.vec = graph_from_adjacency_matrix(vecdist.adj, mode = "undirected")
# modules.vec = fastgreedy.community(mygraph.vec)
# modules.vec = walktrap.community(mygraph.vec)
# print(modules.vec[[3]])
# vecs.mod = vecs[ as.numeric(modules.vec[[3]]), ] 
# vecdist.mod = dist(vecs.mod, method = "manhattan") 
# hc = hclust(as.dist(eldist.mod), method = "single")
#plot(hc)


# save


# modules.vec = getmodules(findModules(1*(vecdist.mat == 2*(seq_size - 1)), iter = 10, sparse = F))
# modules.el = getmodules(findModules(1*(as.matrix(eldist) == 0), iter = 10, sparse = F))

# hc = hclust(vecdist, method = "single")
# plot(hc)
# clusters = cutree(hc, h = 7)
# 
# chunks1 = chunks[clusters == 1]
# chunks2 = chunks[clusters == 2]
# 
# # check 
# 
# vecs1 = vecs[clusters == 1, ]
# vecs2 = vecs[clusters == 2, ]
# 
# vecdist.clus = dist(rbind(vecs1, vecs2), method = "manhattan") 
```




```{r}
# # is reorganizing 3 digits more costly than reorganizing 2?
# maxtransitions = sum(bindistance)
# 
# transitions = melt(bindistance)
# colnames(transitions) = c("from", "to", "value")
# transitions = subset(transitions, value != 0)[-3]
# index = 1
# seq_list = seqs[index, ]
# 
# for (i in 1:maxtransitions){
#   s = subset(transitions, from == index)
#   next_index = s["to"][1, ]
#   if (is.na(next_index)) break
#   print(c(index, next_index))
#   transitions = subset(transitions, !(from == index & to == next_index))
#   transitions = subset(transitions, !(from == next_index & to == index))
#   index = next_index
#   seq_list = rbind(seq_list, seqs[index, ]) 
# }
# print(seq_list)
# print(transitions)
```
